\section*{Awards and Honors}

\subsection*{Active}

\noindent \textbf{Novel Assessments of the Health Impacts of Tropical Cyclones \hfill 2022 - 2027\\ 
NIEHS K99 ES033742 (PI)\\ 
\$954,796}\\
% - PI\\
- Primary Mentor: Prof. Marianthi-Anna Kioumourtozglou\\
- Co-Mentors and collaborators: Profs. Francesca Dominici, G. Brooke Anderson, Carl Vondrik, Diana Hernandez \medskip
% - Collaborator: Prof. Diana Hernandez \medskip

\noindent \textbf{ASPIRE! Peer and Near-Peer Mentoring Program  \hfill 2023} \\
- To support early career faculty researchers from diverse backgrounds at Columbia University Irving Medical Center to enhance retention in academia, promote research career development \medskip

\noindent \textbf{Nomination for Postdoctoral Award  \hfill 2022 - 2023 \\
Blavatnik US Regional Awards}
\medskip

\noindent \textbf{Agents of Change in Environmental Justice Fellow (Cohort 4) \hfill 2022 - 2023\\
Agents of Change in Environmental Justice (no salary coverage)}\\
- Fellowship in cohort of 14 for one year\\
- Founded by Prof. Ami Zota\\
- Cohort to empower emerging leaders from historically excluded backgrounds in science and academia 
- Deliverables include personal essay, podcast and interview %\medskip

\subsection*{Previous}

\noindent \textbf{Reach for the First R01 Workshop \hfill 2022}\\ 
- Competitive course for up promising junior faculty to write and submit successful R01 application \medskip

\noindent \textbf{The Impact of Extreme Heat on Children’s Health in Africa Project \hfill 2020 - 2022\\ 
Columbia University President’s Global Innovation Fund \\
\$45,000 (Co-I; no salary coverage)} \\
% - Co-I\\
- PI: Prof. Lawrence R. Stanberry \\
- Co-Is: Profs. Lisa Saiman, Jane W. Baldwin, Wilmot. G. James \medskip

\noindent \textbf{Climate resilience in Northern Manhattan and the South Bronx: Collaborative, community-led policy research about heat vulnerability in New York City \hfill 2020 - 2021 \\
Columbia University Earth Frontiers) \\ 
\$56,300 (PI; no salary coverage)} \\
% - PI\\
- Co-Is: Prof. Jacqueline Klopp, Sonal Jessel\\
- Collaborated WE ACT to provide insights on heat inequity in NYC during COVID-19 pandemic \\
% - Supervised Graduate Research Assistant Jenny Sing-Bock, who went to become Excelsior Fellow at NYSERDA \medskip

\noindent \textbf{Anomalous temperature and seasonality of mortality in the United States \hfill 2015 - 2019 \\ 
Wellcome Trust \\
\$160,000 }\\
- PhD studentship\\
- Supervised by Profs. Majid Ezzati and Ralf Toumi \medskip

\noindent \textbf{Global Heat Health Information Network (GHHIN) \hfill December 2018\\ 
World Meteorological Organization (WMO)\\
\$3000 }\\
% - UCAR travel grant for travel to GHHIN conference in Hong Kong \\
- Organizing committee for first conference \medskip

\noindent \textbf{1st prize for best presentation \hfill October 2018 \\
Imperial College School of Public Health PhD symposium \\
\$250 }\\
- Annual prize given for best presentation at PhD symposium \medskip

\noindent \textbf{World Meteorological Organization (WMO) Internship \hfill Summer 2017 \\ 
Imperial College London \\
\$5000 }\\
- 3-month internship at WMO Headquarters in Geneva, Switzerland \\
- Supervised by Joy Shumake-Guillemot, Diarmid Campbell-Lendrum \\
- Collaborated with another intern to produce first materials for Global Heat Health Information Network \medskip

% \begin{center} \line(1,0){450} \end{center}

% TEMPLATE

% \noindent \textbf{THING \hfill YEAR - YEAR \\ 
% WHO GAVE ME SOMETHING\\
% \$XXX }\\
% - XX \\
% - XX \medskip
