\section*{Selected Presentations}

\noindent \textbf{Parks RM} (2022). New Frontiers in Climate and Health, \textit{NYU Collaborative Center in Children's Environmental Health Research and Translation Climate Change Interest Group
} \bigskip

\noindent \textbf{Parks RM} (2022). An Introduction to Complex Climate Risks, \textit{MA in Climate and Society, Columbia University} \bigskip

\noindent \textbf{Parks RM} (2022). Novel Assessments of the Health Impacts of Tropical Cyclones, \textit{Climate Change and Health Session, NIEHS EHSCC Annual Meeting} \bigskip

\noindent \textbf{Parks RM}, Casey J (2022). Disaster Medicine: Equitable Health Care in a Changing Climate, \textit{Columbia University} \bigskip

\noindent \textbf{Parks RM}, Benadvides J, Anderson GB, Nethery RC, Navas-Acien A, Dominici F, Ezzati M, Kioumourtzoglou MA (2021). Tropical cyclones and cause-specific mortality in the United States, \textit{ISEE Virtual Conference} \bigskip

\noindent \textbf{Parks RM}, Balilian A, Nunez Y, Hansen J, Raaschou-Nielsen O, Ketzel M, Khan J, Weisskopf MG, Vermeulen R, Peters S, Re DB, Kioumourtzoglou MA (2021). Multi-air pollutant exposure and amyotrophic lateral sclerosis (ALS) diagnosis in Denmark using Bayesian conditional Poisson modelling, \textit{ISEE Virtual Conference} \bigskip

\noindent \textbf{Parks RM} (2021). Climate Change, Hurricanes \& Health,  \textit{Expert Panel Discussion, Boston University, Boston, United States} \bigskip

\noindent \textbf{Parks RM} (2021). Keynote talk on climate, weather, and injuries,  \textit{Virtual Pre-Conference Global Injury Prevention Showcase, Public Health Association of Australia, Adelaide, Australia} \bigskip

\noindent \textbf{Parks RM} (2020). Spatio-temporal modelling to estimate the impact of air pollution, anomalous temperature, coastal storms, and COVID-19 on mortality and morbidity,  \textit{Technical University of Crete, Crete, Greece} \bigskip

\noindent \textbf{Parks RM}, Anderson GB, Nethery RC, Navas-Acien A, Dominici F, Kioumourtzoglou MA (2020). Tropical cyclones and multiple hospitalization outcomes in the United States, \textit{ISEE Virtual Conference} \bigskip

\noindent \textbf{Parks RM} (2020). WE ACT Climate Justice Group knowledge exchange, \textit{WE ACT, New York, United States} \bigskip

\noindent \textbf{Parks RM} (2020). Spatio-temporal modelling to estimate the impact of air pollution, anomalous temperature and coastal storms on mortality and morbidity in the United States,  \textit{IRI, New York, United States} \bigskip

\noindent \textbf{Parks RM} (2019). Air pollution health and policy,  \textit{New York University, New York, United States} \bigskip

\noindent \textbf{Parks RM} (2019). Partciulate matter air pollution and national and county life expectancy loss in the USA: A spatiotemporal analysis,  \textit{Centre for Air Pollution, energy and health research (CAR) webinar series, Sydney, Australia} \bigskip

\noindent \textbf{Parks RM} (2019). Using Bayesian spatio-temporal modelling to estimate the impact of anomalous temperature and air pollution on mortality in the United States,  \textit{Department of Chemical Engineering, Columbia University} \bigskip

\noindent \textbf{Parks RM}, McLaren M, Toumi R \& Rivett U. (2019). Experiences and lessons in managing water from Cape Town. \textit{Making the most of London's waterways, Future of London} \bigskip

\noindent \textbf{Parks RM}, Bennett JE, P, Foreman KJ, Toumi R \& Ezzati M. (2018). Impact of anomalous temperature on injury mortality in the USA.  \textit{ISES-ISEE 2018 Joint Annual Meeting, Ottawa, Canada} \bigskip

\noindent Shumake-Guillemot J, Jones H, \textbf{Parks RM} \& Trtanj J. (2017). Introduction to the Global Heat Health Information Network.  \textit{International Conference of Biometeorology, Durham, UK} \bigskip

\noindent Fernandez Montoya L, \textbf{Parks RM}, \& Shumake-Guillemot J. (2017). Building Health System Resilience to Climate and Environmental Health risks: Insights from Climate Services.  \textit{Strengthening Space Cooperation for Global Health, Geneva, Switzerland} \bigskip

\noindent \textbf{Parks RM}, Bennett JE, P, Foreman KJ, Toumi R \& Ezzati M. (2016). Seasonal dynamics of mortality in the USA from 1982 - 2013. \textit{Bayesian Young Statistician Meeting, Florence, Italy} \bigskip

\noindent \textbf{Parks RM}, Bennett JE, P, Foreman KJ, Toumi R \& Ezzati M. (2016). Seasonality of mortality: identifying patterns and trends with Bayesian spatiotemporal modelling. \textit{International Workshop on Spatiotemporal Statistics, London, UK}

% \begin{center} \line(1,0){450} \end{center}